%-------------------------
% Resume in Latex
% Based on Jake's Resume Template
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage[left=0.5in, right=0.5in, top=0.45in, bottom=0.45in]{geometry}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Busireddy Greeshma} \\ \vspace{4pt}
    \small
    \href{mailto:greeshmab.21@gmail.com}{\underline{greeshmab.21@gmail.com}} $|$
    \href{https://linkedin.com/in/YOUR-URL}{\underline{LinkedIn}} $|$
    \href{https://github.com/greeshmab21}{\underline{GitHub}} $|$
    Remote $\cdot$ Open worldwide
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Final-year CS student (graduating Aug 2026) with hands-on experience building production-grade AI systems --- a real-time clinical AI tool, an agentic workflow engine handling 500+ concurrent requests, and RAG-based document intelligence pipelines. Proficient in Python, FastAPI, LangChain, FAISS, and LLM APIs (Claude, Whisper, Llama). Seeking remote AI/ML or LLM Engineering roles.}

\vspace{-4pt}

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, SQL} \\
     \textbf{AI / ML}{: LangChain, FAISS, Hugging Face, Whisper, Claude API, Llama, Prompt Engineering} \\
     \textbf{Backend}{: FastAPI, Flask, REST APIs, AWS Lambda, AWS S3, Async Python} \\
     \textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Firebase, Supabase} \\
     \textbf{DevOps / Tools}{: Docker, Git, GitHub, Agile/Scrum} \\
     \textbf{Frontend}{: React, HTML, CSS}
    }}
 \end{itemize}

\vspace{-4pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Clinical Blind-Spot Detector} $|$ \emph{Python, FastAPI, Whisper, Claude API} $|$ \href{https://github.com/greeshmab21/clinical-blind-spot-detector}{\underline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Built a real-time clinical AI pipeline streaming live visit audio through Whisper + Claude API to detect unasked screening questions (PHQ-9, AUDIT-C) before the patient leaves.}
            \resumeItem{Validated across 50 simulated transcripts, surfacing 3+ missed blind spots per visit at under 2s end-to-end latency.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Agentic Workflow Execution Engine} $|$ \emph{Python, FastAPI, MongoDB, REST APIs} $|$ \href{https://github.com/greeshmab21/agentic-workflow-execution-engine}{\underline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Orchestrated dynamic AI pipelines handling 500+ concurrent requests at under 200ms latency using async FastAPI with modular REST architecture supporting 8+ pluggable workflow types.}
            \resumeItem{Integrated MongoDB persistence layer enabling stateful task execution and fault-tolerant pipeline recovery across distributed agent workflows.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Retrieval-Augmented Generation (RAG) Q\&A System} $|$ \emph{Python, FAISS, HuggingFace, LangChain} $|$ \href{https://github.com/greeshmab21}{\underline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Delivered context-aware answers across 10K+ document chunks at under 1.5s retrieval latency, improving answer relevance 40\% over baseline keyword search using FAISS + FLAN-T5 semantic embeddings.}
            \resumeItem{Built end-to-end ingestion pipeline using LangChain supporting multi-format documents (PDF, DOCX, TXT) with real-time query handling.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

\vspace{-4pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{Feb 2024 -- May 2024}
      {DeepVisionTech.AI}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Conducted comparative prompt engineering research across multiple LLMs (Bard, early GPT variants), analysing how prompt structure and phrasing affected model output quality and consistency.}
        \resumeItem{Contributed to an AI-powered sign language application using Blender animation pipelines to convert speech into real-time sign language gestures for deaf users.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Full-Stack Developer}{Jan 2024 -- Present}
      {Self-Initiated}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered 15+ client projects over 18 months, building full-stack web applications using Python, FastAPI, Flask, and MySQL --- consistently delivering within 7--10 days per project.}
        \resumeItem{Integrated AI features into client applications based on project needs, managing full delivery lifecycle from requirements gathering to production deployment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RV University}{Bengaluru, India}
      {Bachelor of Technology, Computer Science $|$ CGPA: 7.7/10}{Aug 2022 -- Aug 2026}
  \resumeSubHeadingListEnd

\vspace{-4pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Deep Learning for Developers} --- Infosys Springboard \\
     \textbf{Prompt Engineering} --- Infosys Springboard \\
     \textbf{Introduction to Cybersecurity} --- Cisco
    }}
 \end{itemize}

\end{document}
